---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covidviz

<!-- badges: start -->
<!-- badges: end -->

The goal of covidviz is to provide the user with a set of functions that perform some non-trivial data wrangling and produce plots as results on the [OWID COVID dataset](https://ourworldindata.org/coronavirus-source-data).

## Installation

You can install the development version of covidviz from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tomzhang255/covidviz")
```

## Example

This is an example query:

```{r example1}
library(covidviz)

query1(plot_type = "static", fill = "cases", log_scale = TRUE, projection = "globular")
```

Plot outputs can be dynamic as well:

```{r example2}
query3(plot_type = "dynamic", log_scale = TRUE)
```

There are 6 such queries in total coded as functions. Inspect their documentation by issuing a command of the following form: `?query1`

tests/demo.Rmd contains a collection of function demos.

```{r eval=FALSE, include=FALSE}
# devtools::build_readme()
```
